|

### 2021-10-06 03-Chp-Systematic-Review.Rmd
Draft of chapter 3

The use of the results of this review in subsequent chapters is dicussed.

@@

Several existing reviews do not distinguish between the types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect estimate. However, in this review, the small subset of studies reporting odds/risk ratios and synthesised separately to those reporting hazard ratios.

@@

Results were not combined across different study designs (i.e. RCTs were not combined in a meta-analysis with results from observational studies). The summary effect estimates produced by meta-analysis of individual study designs are discussed, but are compared and contrasted more fully as part of the triangulation exercise presented in Chapter \@ref(discussion-heading)

@@

#### Standard meta-analysis

A straight-forward random-effects meta-analysis model was employed to combine the identified results. A random-effects model was chosen due to the ...

<!-- TODO Finish this description -->

Results were stratified into subgroups on the basis of the overall risk of bias 
assessment, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed. Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line around the overall effect estimate. Finally, a test subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)). All models were implemented using the `metafor` R package.

@@

\blandscape{}
<!----------------------------------------------------------------------------->
(ref:studyCharacteristics-caption) Characteristics of included studies, stratified by study design. Note that three studies reported on multiple analytical designs within a single study, and these have been duplicated across the relevant sub-sections.

@@

As discussed above, the results of the risk-of-bias assessments are presented alongside their corresponding result. A more detailed discussion of the sources and directions of bias is presented in Chapter \@ref(tri-heading), and so this section presents a brief summary of the biases at play.

Following best practice, studies judged to be at critical risk of bias should be excluded from any quantitative analyses. <!-- TODO CITATION NEEDED --> `r num_to_text(n_critical,T)` observational studies were excluded on this basis, predominantly due to a lack of adjustment for any confounders (i.e. the study reported unadjusted estimates).`r critical_citations`

<!-- Both randomised controlled trials were considered to be at low risk of bias.  -->

<!-- For NRSI, common biases include immortal time (where participants in the exposure group are followed up) -->
<!-- For NRSE  -->

<!-- For MR studies, concerns over potential genetic pleiotropy -->

<!-- Additionally, several synthesis were also assessed to be at risk of bias due to missing evidence.  -->

<!-- A key issue identified relating to bias due to missing data was the potential for the search to miss relevant Mendelian randomisation studies which had examined the association between Alzhiemer's disease and multiple risk factors. This is discussed further in Section \@ref(rev-discussion-MR). -->

<!-- Several eligible studies included in the analysis did not have available results, either due to selective reporting of significant results in conference abstracts,[@su2017; @yamada2009b] or due to the unavailability of supplementary materials containing the relevant results.[@haag2009] -->

@@

(ref:statinsRCT-cap) Random effects meta-analysis of randomised controlled trials examining statin statins on all-cause dementia

(ref:statinsRCT-scap) Random effects meta-analysis of statins on all-cause dementia

@@

<!----------------------------------------------------------------------------->
(ref:obsStatinDementia-cap) Random effects meta-analysis of non-randomised studies examining the effect of statin use on all-cause dementia

(ref:obsStatinDementia-scap) Random effects meta-analysis of statins on all-cause dementia

@@

<!----------------------------------------------------------------------------->
(ref:obsFibrateDementia-cap) Random effects meta-analysis of non-randomised studies examining the effect of fibrate use on all-cause dementia

(ref:obsFibrateDementia-scap) Random effects meta-analysis of statins on all-cause dementia

@@

@@

`r obsHyperchol$Dementia$n` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$Dementia$estimate`, Figure \@ref(fig:obsHyperDementia)).

<!----------------------------------------------------------------------------->
(ref:obsHyperDementia-cap) Random effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on all-cause dementia

(ref:obsHyperDementia-scap) sMeta-analysis of hypercholesterolemia on all-cause dementia

@@

<!----------------------------------------------------------------------------->
(ref:lipidFractionsDementia-cap) Random effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on all-cause dementia risk, standardised per 1-SD increase in the lipid fraction.

(ref:lipidFractionsDementia-scap) Random effects meta-analysis of four lipid fractions on all-cause dementia
```{r lipidFractionsDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsDementia-cap)', out.width='100%', fig.scap='(ref:lipidFractionsDementia-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/fp_lipids_composite_Dementia.pdf"))
```
<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->
(ref:obsStatinAD-cap) Random effects meta-analysis of non-randomised studies examining the effect of statin use on Alzheimer's disease

(ref:obsStatinAD-scap) Random effects meta-analysis of statins on Alzheimer's disease

@@

<!----------------------------------------------------------------------------->
(ref:mrStatinAD-cap) Random effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease

(ref:mrStatinAD-scap) Random effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease

@@

<!----------------------------------------------------------------------------->
(ref:obsHyperAD-cap) Random effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on Alzheimer's disease

@@

<!----------------------------------------------------------------------------->
(ref:lipidFractionsAD-cap) Random effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on Alzheimer's disease risk, standardised per 1-SD increase in the lipid fraction.

(ref:lipidFractionsAD-scap) Random effects meta-analysis of four lipid fractions on Alzheimer's disease

@@

<!----------------------------------------------------------------------------->
(ref:obsStatinVaD-cap) Random effects meta-analysis of non-randomised studies examining effect of statin use on vascular dementia

(ref:obsStatinVaD-scap) Random effects meta-analysis of statins on vascular dementia

```{r obsStatinDVaDFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinVaD-cap)', out.width='100%', fig.scap='(ref:obsStatinDVaD-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_VaD.png"))
```
<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->
(ref:obsHyperVaD-cap) Random effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on vascular dementia

@@

<!----------------------------------------------------------------------------->
(ref:lipidFractionsVaD-cap) Random effects meta-analysis of total cholesterol on vascular dementia, standardised per 1-SD increase in the lipid fraction.

(ref:lipidFractionsVaD-scap) Random effects meta-analysis of total cholesterol on vascular dementia

@@

### Sources of heterogeneity

Data on another potentially important source of heterogeneity.

Plus other such as education level and baseline cognitive scores, but data were either not reported for most studies or when reported, were too diverse to synthesize.

<!-- TODO Can only do meta-regression in analysis with 10 studies, so statins and hypercholesterolemia should -->

Across all analysis with

<!-- Detail that some of these are exploratory, in particular the effect of different scales on the association between the groups. **[CROSS]** -->

<!-- Important here to examine effect of risk of bias (due to immortal time in observational studies). -->

<!-- Also important to examine the effect of: -->

<!-- * age at baseline -->
<!-- * sex (percentage) -->
<!-- * education -->
<!-- * baseline cognitive scores (how to group) -->

<!-- ### Sensitivity analyses -->

### Small study effects {#sys-rev-pub-bias}

<!--    Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were -->
<!--    Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published studies difficult -->

There was little evidence of small study effects across the evidence base (Figure \@ref(fig:funnelStatinsAny)).

@@

<!-- <!-----------------------------------------------------------------------------> -->
<!-- (ref:preprintWeights-caption) Amount of information added by inclusion of preprinted results, estimated from the weight assigned to the study in a random-effect meta-analysis  -->

@@

<!-- ```{r preprintWeights-table, message=FALSE, results="asis", echo = FALSE} -->
<!-- ``` -->
<!-- <!-----------------------------------------------------------------------------> -->

@@

<!----------------------------------------------------------------------------->
(ref:typeByYear-cap) __Study designs by year of publication__ -

@@

Finally in terms of generalisability, despite a large proportion of included studies being conducted in the Western world (Figure \@ref(fig:)), the applicability of my results to other populations is aided by th inclusion of studies which made use of data from the Taiwan health insurance database.

@@

<!----------------------------------------------------------------------------->
(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the number of hits returned by each is expected.

>>>>

The added value of including preprinted study reports, made possible using the tool described in the previous chapter, along with the use of the results of this review in subsequent chapters, is discussed.

@@

Several existing reviews do not distinguish between the types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect estimate. However, in this review, the small subset of studies reporting odds/risk ratios are synthesised separately to those reporting hazard ratios.

@@

Results were not combined across different study designs (i.e. RCTs were not combined in a meta-analysis with results from observational studies). The summary effect estimates produced by meta-analysis of individual study designs are discussed, but are compared and contrasted more fully as part of the triangulation exercise presented in Chapter \@ref(discussion-heading).

@@

#### Random-effects meta-analysis

For results examining the effect of binary or continuous exposure (as opposed to categorical/dose-response, as discussed in the next section) on any dementia outcome, a random-effects meta-analysis model was used. Random-effects meta-analysis does not assume one true underlying effect, but rather allows for a distribution of true effects with variance $\tau^2$. The weight ($w$) assigned to each result (denoted as $y_i$) is then give as the inverse of variance of that result plus the estimate of between-result variance, denoted as $w_i = \frac{1}{v_i+\tau^2}$ for result $i$.

Once the weights are calculated for each result, the overall estimate ($\hat{y}$) and variance ($Var(\hat{y})$) can be estimated:

\begin{equation}
\hat{y} = \frac{\sum{y_iw_i}}{\sum{w_i}}
  (\#eq:rmaEstimate)
\end{equation}

\begin{equation}
Var(\hat{y}) = \frac{1}{\sum{w_i}}
  (\#eq:rmaVariance)
\end{equation}

Results were stratified into subgroups on the basis of the overall risk of bias assessment, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed in each forest plot. Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line banding the overall effect estimate. Finally, where at least 10 results are available, a test subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)). All models were implemented using the `metafor` R package.

@@

\blandscape{}
<!----------------------------------------------------------------------------->
(ref:studyCharacteristics-caption) Characteristics of included studies, stratified by study design. Note that three studies reported on multiple analytical designs within a single study report, and these have been duplicated across the relevant sub-sections.

@@

As discussed above, the risk-of-bias assessments are presented alongside their corresponding numerical result. A more detailed discussion of the sources and directions of bias is presented in Chapter \@ref(tri-heading), and so this section presents a brief summary of the biases observed in each study design.

For the two randomised controlled trials, both were judged to be at low risk of bias. In contrast, many of the non-randomised studies of statin use were at serious risk of bias due poor controlling for confounding, immortal time bias, and missing outcome data (as noted above, a judgement of low risk of bias for a non-randomised study is rare). Similarly, non-randomised studies of exposures suffered from incomplete adjustment for potentially important confounders, and concerns over the selection of the reported result from among several analyses (e.g. examination of lipids as a binary or continuous variable). Finally, bias was introduced into Mendelian randomisation studies via the potential for hoziontal pleiotropy and population stratification.[@davies2018]

Following best practice, any result judged to be at critical risk of bias should be excluded from any quantitative analyses. <!-- TODO CITATION NEEDED --> `r num_to_text(n_critical,T)` observational studies were excluded on this basis, predominantly due to a lack of adjustment for any potentially important confounders (i.e. the study reported unadjusted estimates).`r critical_citations`

@@

(ref:statinsRCT-cap) Random-effects meta-analysis of randomised controlled trials examining statin statins on all-cause dementia

(ref:statinsRCT-scap) Random-effects meta-analysis of statins on all-cause dementia

@@

<!----------------------------------------------------------------------------->
(ref:obsStatinDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on all-cause dementia

(ref:obsStatinDementia-scap) Random-effects meta-analysis of statins on all-cause dementia

@@

<!----------------------------------------------------------------------------->
(ref:obsFibrateDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of fibrate use on all-cause dementia

(ref:obsFibrateDementia-scap) Random-effects meta-analysis of statins on all-cause dementia

@@

<!-- TODO Deal with awkward hypercholesterolemia definition -->

@@

`r num_to_text(obsHyperchol$Dementia$n,T)` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$Dementia$estimate`, Figure \@ref(fig:obsHyperDementia)).

<!----------------------------------------------------------------------------->
(ref:obsHyperDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on all-cause dementia

(ref:obsHyperDementia-scap) Meta-analysis of hypercholesterolemia on all-cause dementia

@@

<!----------------------------------------------------------------------------->
(ref:lipidFractionsDementia-cap) Random-effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on all-cause dementia risk, standardised per 1-SD increase in the lipid fraction.

(ref:lipidFractionsDementia-scap) Random-effects meta-analysis of four lipid fractions on all-cause dementia
```{r lipidFractionsDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsDementia-cap)', out.width='100%', fig.scap='(ref:lipidFractionsDementia-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/fp_lipids_composite_Dementia.pdf"))
```
<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->
(ref:obsStatinAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on Alzheimer's disease

(ref:obsStatinAD-scap) Random-effects meta-analysis of statins on Alzheimer's disease

@@

<!----------------------------------------------------------------------------->
(ref:mrStatinAD-cap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease

(ref:mrStatinAD-scap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease

@@

<!----------------------------------------------------------------------------->
(ref:obsHyperAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on Alzheimer's disease

@@

<!----------------------------------------------------------------------------->
(ref:lipidFractionsAD-cap) Random-effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on Alzheimer's disease risk, standardised per 1-SD increase in the lipid fraction.

(ref:lipidFractionsAD-scap) Random-effects meta-analysis of four lipid fractions on Alzheimer's disease

@@

<!----------------------------------------------------------------------------->
(ref:obsStatinVaD-cap) Random-effects meta-analysis of non-randomised studies examining effect of statin use on vascular dementia

(ref:obsStatinVaD-scap) Random-effects meta-analysis of statins on vascular dementia

```{r obsStatinVaDFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinVaD-cap)', out.width='100%', fig.scap='(ref:obsStatinDVaD-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_VaD.png"))
```
<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->
(ref:obsHyperVaD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on vascular dementia

@@

<!----------------------------------------------------------------------------->
(ref:lipidFractionsVaD-cap) Random-effects meta-analysis of total cholesterol on vascular dementia, standardised per 1-SD increase in the lipid fraction.

(ref:lipidFractionsVaD-scap) Random-effects meta-analysis of total cholesterol on vascular dementia

@@

### Additional analyses

Investigation of potential sources of heterogeneity was complicated by two factors. In the first instance, few meta-analysis included more than 10 results, the recommended minimum. Secondly, poor reporting of summary statistics including education level and baseline cognitive ability precluded the use of several results in a meta-regression analysis.

Age and sex were assessed as potential causes of heterogeneity for meta-analysis of statin use and hypercholesterolemia on all cause dementia and Alzheimer's disease, but I found very weak evidence for variation in the observed effect estimates due to these factors.

Similarly, assessment of small-study effects, for which publication bias could be one potential reason, was hindered by the relatively small number of results included in a given meta-analysis. However, all analyses assessed provided weak evidence of small-study effects.

[_Note: Julian, is this sufficient or should I report statistics for each? Additionally, are there any other sensitivity analyses I should be presenting here?_]

@@

<!----------------------------------------------------------------------------->
<!-- (ref:preprintWeights-caption) Amount of information added by inclusion of preprinted results, estimated from the weight assigned to the study in a random-effect meta-analysis  -->

@@

<!-- ```{r preprintWeights-table, message=FALSE, results="asis", echo = FALSE} -->
<!-- ``` -->
<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->
(ref:typeByYear-cap) Included study designs by year of publication

@@

Finally in terms of generalisability, despite a large proportion of included studies being conducted in the Western world (Figure \@ref(fig:cohortLocations)), the applicability of the results to other populations is aided by the inclusion of studies which made use of data from the Taiwan health insurance database.

@@

<!----------------------------------------------------------------------------->
(ref:preprintGrowth-cap) Growth of preprint repositories over time. Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the number of hits returned by each is expected.
